---
title: "CMS"
author: "Harshitha Sriramoju"
date: "2024-08-21"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r message=FALSE, warning=FALSE}

library(dplyr)
library(ggplot2)
library(mosaic)
library(tidyverse)
library(knitr)
library(tidyr)
```


*Datasets in question:*
*Hospital Data: https://data.cms.gov/provider-data/topics/hospitals*
Long-Term Care Facility Characteristics : https://data.cms.gov/quality-of-care/long-term-care-facility-characteristics
Nursing Homes including rehab services: https://data.cms.gov/provider-data/topics/nursing-homes


```{r}
long_term_facility<- read.csv("C:/Users/harsh/Downloads/Long_Term_Care_Facility_Characteristics_Q1_2024.csv")
```

```{r}
summary(long_term_facility)
```


```{r}
str(long_term_facility)
```

```{r}
missing_values <- colSums(is.na(long_term_facility))
print(missing_values)
```



```{r}
numeric_cols <- select(long_term_facility, where(is.numeric))
numeric_cols %>% 
  gather(key = "variable", value = "value") %>% 
  ggplot(aes(x = value)) +
  geom_histogram(bins = 30) +
  facet_wrap(~ variable, scales = "free_x") +
  theme_minimal()
```


*Another Dataset*



```{r}
pbj_home<- read.csv("C:/Users/harsh/Downloads/Long_Term_Care_Facility_Characteristics_Q1_2024.csv")

```

```{r}
summary(pbj_home)
```

```{r}
str(pbj_home)
```

```{r}
numeric_cols <- select(pbj_home, where(is.numeric))
numeric_cols %>% 
  gather(key = "variable", value = "value") %>% 
  ggplot(aes(x = value)) +
  geom_histogram(bins = 30) +
  facet_wrap(~ variable, scales = "free_x") +
  theme_minimal()
```
```{r}
hospital_data<- read.csv("C:/Users/harsh/Downloads/HCAHPS-Hospital.csv")
```

```{r}
summary(hospital_data)
```

*Analyzing star rating across hospitals*

Insufficient data due to the overwhelming amoung of NA values. Difficult to analyze and assume.


```{r}
# Convert Patient.Survey.Star.Rating to numeric
hospital_data <- hospital_data %>%
  mutate(Patient.Survey.Star.Rating = as.numeric(as.character(Patient.Survey.Star.Rating)))

# Remove rows where star rating is NA
star_rating <- hospital_data %>%
  filter(!is.na(Patient.Survey.Star.Rating))

# Calculate the mean of the star rating
mean_star_rating <- mean(star_rating$Patient.Survey.Star.Rating, na.rm = TRUE)



```

*Mean star rating is about 3.25 across the hospitals listed.*

Link below has meaningful charts based on Nursing Survey Responses.

*ANA’s Workforce Surveys*

https://www.nursingworld.org/practice-policy/work-environment/health-safety/disaster-preparedness/coronavirus/what-you-need-to-know/covid-19-survey-series-anf-2022-workplace-survey/

*2022 National Nursing Workforce Survey*
https://www.journalofnursingregulation.com/article/S2155-8256(23)00047-9/fulltext


*Why are nurses quitting?*
https://www.ncbi.nlm.nih.gov/pmc/articles/PMC11004833/#:~:text=Nurses%20who%20were%20employed%20but,22%25%5D)%3B%20and%20unsafe     